Your Paper Title

### 2025-03-28 paper/paper.qmd
update paper margins and enhance bibliography entries; clarify reference details

---
title: "Your Paper Title"
subtitle: "So fancy!"
author:
    - Luca Carnegie
    - Chris Lu
    - Russell Luchin
    - Randall Ni
abstract:
    This is the abstract of your paper. Write a brief summary of your research,
    including your objectives, methods, key results, and main conclusions.
    Keep it concise but informative.
keywords: [keyword1, keyword2, keyword3]
format:
    pdf:
        documentclass: article
        papersize: letter
        toc: true
        number-sections: true
        colorlinks: true
        fig-cap-location: bottom
        tbl-cap-location: top
        geometry: "margin=1in"  
bibliography: references.bib
execute:
    echo: false  # Hide code by default
    warning: false
    message: false
    jupyter: "python"
---

>>>>

---
title: "Your Paper Title"
subtitle: "So fancy!"
author:
    - Luca Carnegie
    - Chris Lu
    - Russell Luchin
    - Randall Ni
abstract:
    This is the abstract of your paper. Write a brief summary of your research,
    including your objectives, methods, key results, and main conclusions.
    Keep it concise but informative.
format:
    pdf:
        documentclass: article
        papersize: letter
        toc: true
        number-sections: true
        colorlinks: true
        fig-cap-location: bottom
        tbl-cap-location: top
        geometry: "margin=1in" # print margins (change if wanting to)
bibliography: references.bib
execute:
    echo: false  # Hide code by default
    warning: false
    message: false
    jupyter: "python"
nocite: "@*" # display all references by default
thanks: "Code and workflow available at: https://github.com/lcarnegie/sakura" 
---
